\begin{titlepage}
    \thispagestyle{empty} % Remove page numbers
    \setstretch{1.5} % Line spacing, make sure the setspace package is included in document.tex

    \begin{center}
        \textbf{\Large ABSTRACT}
    \end{center}

    \vspace{1cm} % Vertical space

    \noindent CAGIDE FIALHO, G. Report on the Modeling and Control Systems Project. 2024. \pageref{LastPage} p. Final Project for the Modeling and Control Systems Course (Bachelor’s degree in Computer Engineering) - Bachelor’s Degree in Computer Engineering, State University of Rio de Janeiro, Nova Friburgo, 2024.

    \vspace{0.4cm} % Vertical space

    This work explores the modeling and control of a dynamic system of the mass-spring-damper type, using the Scilab platform for development and simulation. The focus of the study is on implementing mathematical models to describe the system dynamics and analyzing its response under various initial conditions without the application of external forces. Using Xcos, a graphical component of Scilab, we conducted simulations that allowed for visual and quantitative analysis of the system's transient responses. The study highlights the influence of physical parameters, such as mass, damping coefficient, and spring constant, on the system's response characteristics. Furthermore, control techniques were employed to adjust the system's response, demonstrating how damping can contribute to stabilization after disturbances and emphasizing the importance of careful parameterization to achieve effective system behavior. This project contributes to the understanding of control theories applicable to mechanical systems and other dynamic system contexts in engineering.
    \vspace{0.4cm} % Vertical space

    \textbf{Keywords}: Modeling and Control, Mass-Spring-Damper System, Simulation, Scilab, Xcos.
\end{titlepage}
